\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage{fbb}

\begin{document}
\title{ULUG Constitution}

\section{Article I --- Name and Purpose}

The USLUG or USLUG Student Linux User Group is a Linux Users Group
(LUG). Our purpose as a Linux User's Group is to provide an environment
to facilitate learning of the GNU/Linux system and all free/open source
software.

\paragraph{This includes but is not limited to the following:}

\begin{itemize}
	\item
		Providing support users in the use of free/open source software
	\item
		Promoting the use of free/open source software
	\item
		Promoting freedom both inside and outside of software development
	\item
		Contributing to the open source community
\end{itemize}

\section{Article II --- Membership}

To become a member you must meet the following qualifications:

\subsection{Member Qualifications}

\begin{itemize}
	\item
		Be a student at the University of Utah
\end{itemize}

\subsection{Full-Voting Member}

\begin{itemize}
	\item
		Attend half of the meetings
\end{itemize}

\section{Article III --- Meeting}

Regular meetings will be held every other week. The schedule of these
meetings will be decided by majority vote at the beginning of each
semester.

To call a unscheduled meeting, one must announce the meeting on the
mailing list.

\section{Article IV --- Executive
Board}

\subsection{President}

\begin{itemize}
	\item
		The duties of the president will be to preside over the meetings and
		facilitate in organizing the group.
	\item
		The president will preside at the meetings.
	\item
		If there is a vacancy midterm, the vice president will take the role
		of president.
\end{itemize}

\subsection{Vice President}

\begin{itemize}
	\item
		The vice president will work with the president in a equal partnership
		in organizing the group and will preside over meetings in the
		presidents absence.
	\item
		If there is a vacancy in the vice president position, a special
		election will be held for that position.
\end{itemize}

\subsection{Treasurer}

\begin{itemize}
	\item
		The Treasurers duties will include keeping track of the groups
		finances.
	\item
		If there is a vacancy in the Treasurer position elections will be
		held.
\end{itemize}

\section{Article V --- Elections}

\begin{itemize}
	\item
		Elections will be held once every other semester.
	\item
		There will be no nominations. Any full member can run for a position.
	\item
		The full membership will vote on the positions and who ever obtains
		the most votes will win.
	\item
		In the case of a tie, the member with the most attendance will win the
		role.
\end{itemize}

\section{Article VI --- Funds}

The allocation of funds will be based on the majority vote of the group.

\section{Article VII --- Advisor}

Advisors will participate as they see fit and provide guidance for the
group.

\section{Article VIII --- Ratification}

The constitution will be ratified by the founding members. For
ratification there must be unanimous agreement.

\section{Article IX --- Amendments}

Amendments will be presented to the membership by any full member and
will be voted on by the membership. For this there must be a
supermajority. In this case a supermajority means 75 percent or greater
must be in favor of the ammendment. Only full members can vote.
\end{document}
